### 2018-10-19 manuscript.rmd
checking taxon name reconciliation

ggplot() + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect(data=D, mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) + 
	scale_fill_discrete(guide = guide_legend(reverse=TRUE))
```

@@

>>>>

ggplot() + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect(data=D, mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) + 
	# scale_fill_manual(guide = guide_legend(reverse=TRUE))
	# scale_fill_manual(values = clade_colors, guide = guide_legend(reverse=TRUE))
	scale_fill_discrete(guide = guide_legend(reverse=TRUE))
```

@@

## Matrix mapping

Taxa and partition correspondence across manuscripts was assessed by comparing all sequences for each taxon in each partition across all matrices with diamond blast. Based on inspection of sequence similarity, we excluded all comparisons with less than 99% identity and greater than 10^-25^ e-value.

### Taxa

The primary intent of comparing taxa across matrices was to validate our taxon name reconciliation across studies.

We first considered pairwise similarity between the same species from different matrices in different studies.

```{r taxon_mapping_across_studies}

Dtaxaxman = 
	read_tsv("~/Dropbox/repo/animal_root/blast/graphs/cross_mscript_taxa.tsv") %>%
	arrange( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2 )

Dtaxaxman_raw_count = nrow(Dtaxaxman)

Dtaxaxman %<>%
	distinct( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2, .keep_all = TRUE )

`r Dtaxaxman_raw_count` raw pairwise comparisons passed the similarity thresholds under these sampling criteria. These included multiple hits for the same sequence pairs from different regions. When only a single hit is retained, there are `r nrow(Dtaxaxman)` retained sequence pairs.

We next considered taxon mapping more generally.

```{r taxon_mapping}

Dtaxa = 
	read_tsv("~/Dropbox/repo/animal_root/blast/graphs/taxon_graph.tsv") %>%
	arrange( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2 )

# Set aside species correspondense to same species in same matrix in same matrix
Dtaxa_self =
	Dtaxa %>%
		filter( mscript1 == mscript2 & dataset1==dataset2 & taxon1==taxon2  )

# Remove species correspondense to same species in same matrix in same study
Dtaxa %<>%
	filter( !(mscript1 == mscript2 & dataset1==dataset2 & taxon1==taxon2) )

n_not_self = nrow(Dtaxa)

# Remove hits in same matrix in same study
Dtaxa %<>%
	filter( !(mscript1==mscript2 & dataset1==dataset2))

# Remove hits same study, presume that taxon resolution is OK within study.
Dtaxa %<>%
	filter( !(mscript1==mscript2))

ggplot(Dtaxa) + geom_density(aes(count)) + xlim(0,50)

ggplot(Dtaxa_self) + geom_density(aes(count))

# These are candidates for renaming
Dtaxa %>% filter(taxon1!=taxon2) %>% arrange( desc(count))

### Partitions
